---
title: "Homework 5"
author: "Sarah Younes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As always, I will begin by loading the packages I will need for this assignment: tidyverse. I will also use `set.seed` so that I get the same values in Problem 3 when I generate data sets.

```{r load packages and set seed, message = FALSE}
library(tidyverse)
set.seed(1)
```

## Problem 1

First, I will import the data.

```{r raw data}
homicide_data =
  read.csv("./data/homicide-data.csv")
```

Next, I will clean the data.

```{r cleaning data}
homicide_data =
  homicide_data |>
  janitor::clean_names() |>
  mutate(
    victim_last = str_to_title(victim_last),
    victim_first = str_to_title(victim_first)) |>
  mutate(city_state = paste(city, state, sep = ", "))
```

Now, I will summarize within cities to obtain the total number of homicides and the total number of unsolved homicides, and I will show both of these values for each city.

```{r city summaries}
total_homicides =
  homicide_data |>
  group_by(city) |>
  summarize(
    total_homicides = n())

unresolved_homicides =
  homicide_data |>
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") |>
  group_by(city) |>
  summarize(
    unresolved_homicides = n())

city_summaries =
  full_join(total_homicides, unresolved_homicides, by = "city") |>
  print(n = Inf)
```

## Problem 2

First, I will start with a data frame containing all file names.

```{r file names}
csv_files =
  list.files(path = "./data/problem_2", pattern = "\\.csv$", full.names = TRUE)

csv_files_df =
  csv_files |>
  tibble()
```

First, I will create a data frame containing all file names via `list.files` and paths. Then, I will use `purrr::map` to import each csv file into the data frame, and all their data is saved as a new `data` variable in the data frame.

```{r importing data, message = FALSE, warning = FALSE}
df =
  tibble(
    files = list.files("./data/problem_2/", pattern = "\\.csv$"),
    path = str_c("./data/problem_2/", files)) |>
  mutate(
    data = purrr::map(path, read_csv))

df
```

Next, I will clean the data to unnest all the weekly data from the `data` variable, create ID and study arm variables,tidy the week variable, set `week` as a numeric value, and select the variables I need.

```{r tidying}
tidy_df =
  df |>
  unnest(cols = c(data)) |>
  mutate(
    id = str_extract(files, "\\d+"),
    arm = str_extract(files, "con|exp")) |>
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value") |>
  mutate(
    week = as.numeric(week)) |>
  select(id, arm, week, value)

tidy_df
```

Now, I will make a spaghetti plot showing the observations for each subject over time by study arm/treatment group (experimental vs. control). Most study participants started around the same values. The control group remained mostly the same over the 8 weeks whereas the experimental arm saw larger improvements, which indicates there was likely not a placebo effect among the control group.

```{r spaghetti plot}
tidy_df |>
  ggplot(aes(x = week, y = value, color = id)) +
  geom_line() +
  facet_grid(. ~ arm, labeller = labeller(arm = c(con = "Control group", exp = "Experimental group"))) +
  labs(
    x = "Week",
    y = "Observation value",
    title = "Observations over time by subject ID and treatment group",
    color = "Subject ID")
```

## Problem 3

```{r}
t_test_simulations = function(n = 30, mu = 0, sigma = 5, simulations = 5000) {
  
    data =
      tibble(
        x = rnorm(n = n, mean = mu, sd = sigma))

    t_test =
      t.test(data, mean = 0, conf.level = 1 - 0.05) |>
      broom::tidy()
    
  }
```

```{r}
output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = t_test_simulations(30)
}

sim_results = bind_rows(output)
```